\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-11-13 Manuscript/Manuscript.tex
added discussion section

>>>>

The findings from this survey paper show the multifaceted approaches being taken in the field of research into cycling infrastructure, and how important they are to encourage sustainable urban transportation. In this discussion section will include; key themes, criticisms, and potential future pathways for similar research. \par

The different types of cycling infrastructure, especially bike lanes, are shown in this body of research to have a significant impact on increasing cycling ridership. Whether it's an increase in bike-shares or commutership, this relationship is shown in the papers. This is essential when it comes to appealing to policy makers and decision makers in communities to convince them to add cycling infrastructure to their area. Statistical analyses are influential in providing actionable insights, including the correlation between infrastructure types existing in an area and increased cycling. \par

Studies like \citet{1MateoBabiano2016} show how effective simple methods like Spearman's correlation coefficient can be at revealing the impact of bike lanes on PBSP usage. These sorts of results can lead to insights for urban planners when it comes to designing cities. \par

Predictive models were also used, like binary regression models in \citet{2Yujun2019} to provide insight into all the factors influencing an individuals' choice to cycle for commuting. These predictive models offer ways for policy makers to encourage cycling as a successful commuting option in their cities.\par

Some future directions this field could go include focusing on more that just high socioeconomic areas. This type of research has only really been done in affluent countries, likely because a lot of the research has been based off of bike-share systems. Which leads into another point of improvements, where there could be better ways of collecting data on cyclists, as they are often excluding people who own their own bikes from the data. Additionally, there is room for more cost-benefit analyses on the economic impact of investing in cycling infrastructure. When you create such infrastructure, there could be less congestion and damage to the automobile infrastructure. Which would be beneficial to persuading policy makers towards creating more bike lanes and encouraging cycling.
